Bayesian Deep Gaussian Processes for Correlated Functional Data: \\ A Case Study in Cosmological Power Spectra

### 2025-06-06 paper/main.tex
update r options to 5 and 15

For each simulated function and variance specification, we generate 20 values of 
$m_1, m_2, f_1, f_2$, and conditional on these values, we sample either 5 or 20 
functional observations and estimate the underlying true function based on the observations.

\begin{figure}[t]
    \centering
    \includegraphics[width=6in]{sims_logS.png}
    \caption{Boxplot of log scores across two different functions and covariance 
             settings (lower is better). For each case, the boxplot is constructed 
             from 20 random batches were simulated. Each column represents a function/variance 
             specification pair, and each row shows results for batch sizes of either 
             5 (top) or 20 (bottom).}
    \label{fig:sims_logS}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=6in]{sims_MSE.png}
    \caption{Boxplot of MSEs across two different functions and covariance settings 
             (lower is better). For each case, the boxplot is constructed from 20 
             random batches were simulated. Each column represents a function/variance 
             specification pair, and each row shows results for batch sizes of 
             either 5 (top) or 20 (bottom).}    
    \label{fig:sims_MSE}
\end{figure}

>>>>

For each simulated function and variance specification, we generate 20 values of 
$m_1, m_2, f_1, f_2$, and conditional on these values, we sample either 5 or 15 
functional observations and estimate the underlying true function based on the observations.

\begin{figure}[t]
    \centering
    \includegraphics[width=6in]{sims_logS.png}
    \caption{Boxplot of log scores across two different functions and covariance 
             settings (lower is better). For each case, the boxplot is constructed 
             from 20 random batches were simulated. Each column represents a function/variance 
             specification pair, and each row shows results for batch sizes of either 
             5 (top) or 15 (bottom).}
    \label{fig:sims_logS}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=6in]{sims_MSE.png}
    \caption{Boxplot of MSEs across two different functions and covariance settings 
             (lower is better). For each case, the boxplot is constructed from 20 
             random batches were simulated. Each column represents a function/variance 
             specification pair, and each row shows results for batch sizes of 
             either 5 (top) or 15 (bottom).}    
    \label{fig:sims_MSE}
\end{figure}
